%\documentclass[twoside,hidelinks]{ctuthesis}
\documentclass[twoside]{ctuthesis}
\usepackage{adjustbox}
\usepackage{fancyvrb}

\ctusetup{
    xdoctype = B,
    xfaculty = F3,
    mainlanguage = english,
    titlelanguage = english,
    secondlanguage=czech,
    otherlanguages = {czech},
    title-english = {Application for personal development},
    title-czech = {Aplikace pro podporu osobního rozvoje},
    keywords-english = {personal development, competitiveness},
    keywords-czech = {osobní rozvoj, soutěživost},
    author = {Artem Vanyukhin},
    supervisor = {Ing. Pavel Náplava, Ph.D.},
    fieldofstudy-english = {Software Engineering and Technology},
    day = 20,
    month = 5,
    year = 2021,
    front-specification = true,
    specification-file = zadani.pdf,
}

\ctuprocess

\begin{thanks}
    I would like to thank my supervisor Ing.\ Pavel Náplava, Ph.D.\ for his guidance and valuable input.
    I would like to thank my friends for their feedback: Sofya Lartseva, Ryan Awo, Jelizaveta Zimina, Chistiaan Dekkers, Nail Al-Gadyan.
\end{thanks}

\begin{declaration}
    I hereby declare that the present thesis was composed by myself and was not previously included in a thesis or dissertation.

    In Prague on \monthinlanguage{title} \ctufield{day}, \ctufield{year}
\end{declaration}

\begin{abstract-english}
%    This paper will analyze the domain of personal development and set up criteria for a new application.
%    Existing solutions will be analyzed based on these criteria.
%    It will also analyze the usage of competitiveness as a motivation for personal development.
%    Analysis for the new application will be proposed based on the performed research.
    This paper researches the domain of personal development and possibility of using competitiveness as a motivation for personal development.
    Performed research serves as a basis for the analysis of existing solutions and proposition of a new application.
\end{abstract-english}

\begin{abstract-czech}
%    Táto práce provede analýzu domény osobního rozvoje a definuje kritéria pro novou aplikaci.
%    Na základě těchto kritérií budou analyzována existující řešení.
%    Také bude analyzována možnost využiti soutěživosti jako nástroje osobního rozvoje.
%    Na základně provedené rešerší bude navržená analýza nové aplikace.
    Tato práce se zabývá rešerši domény osobního rozvoje a možnosti využití soutěživosti k motivaci osobního rozvoje.
    Provedená rešerše slouží základem k analýze existujících řešení a následujícímu návrhu nové aplikace.
\end{abstract-czech}

\begin{document}

    \maketitle
    \input{chapters/introduction.tex}

%    Personal development domain
    \input{chapters/chapter02.tex}

%    Existing solutions
    \input{chapters/chapter03.tex}

%    Solution analysis
    \input{chapters/chapter04.tex}

%    Implementation
    \input{chapters/chapter05.tex}

%    Testing
    \input{chapters/chapter06.tex}

    \input{chapters/conclusion.tex}

%    \input{chapters/appendix.tex}

    \bibliographystyle{amsalpha}
    \begin{thebibliography}{99}
        \bibitem{maslow-motivation}
        A. Maslow.
        \href{http://psychclassics.yorku.ca/Maslow/motivation.htm}{\emph{"A theory of human motivation."}}
        Psychological Review, 1943.
        \bibitem{maslow-pyramid}
        \href{https://en.wikipedia.org/wiki/File:Maslow's_Hierarchy_of_Needs2.svg}{\emph{"Maslow's hierarchy of needs."}}
        Wikipedia.org, 2020.
        \bibitem{what-is-personal-development}
        \href{https://www.skillsyouneed.com/ps/personal-development.html}{\emph{What is Personal Development?}}
        skillsyouneed.com, 2020.
        \bibitem{the-four-faces-of-competetition}
        Orosz G, Tóth-Király I, Büki N, Ivaskevics K, Bőthe B and Fülöp M
        \href{https://www.frontiersin.org/articles/10.3389/fpsyg.2018.00779/full}{\emph{"The Four Faces of Competition: The Development of the Multidimensional Competitive Orientation Inventory."}}
        Front.Psychol., 2018.
        \bibitem{cit-ryckman-hca}
        Ryckman, R. M., Libby, C. R., van den Borne, B., Gold, J. A., and Lindner, M. A.
        \href{https://doi.org/10.1080/00223891.1990.9674097}{\emph{"Construction of a Hypercompetitive Attitude Scale."}}
        Journal of Personality Assessment, Vol.62, 1994.
        \bibitem{cit-ryckman-pdca}
        Ryckman, R. M., Hammer, M., Kaczor, L. M., and Gold, J. A.
        \href{https://doi.org/10.1207/s15327752jpa6602_15}{\emph{"Construction of a personal development competitive attitude scale."}}
        Journal of Personality Assessment, Vol.66, 1996.
        \bibitem{cit-ryckman-adca} Ryckman, R. M., Thornton, B., and Gold, J. A.
        \href{https://doi.org/10.3200/JRLP.143.2.175-192}{\emph{"Assessing Competition Avoidance as a Basic Personality Dimension."}}
        The Journal of Psychology, Vol.143, 2009.
        \bibitem{mobile-vs-desktop}
        BroadbandSearch.net,
        \href{https://www.broadbandsearch.net/blog/mobile-desktop-internet-usage-statistics}{\emph{"Mobile Vs. Desktop Internet Usage (Latest 2020 Data)."}}
        www.broadbandsearch.net, 2020.
        \bibitem{uloo-logo}
        Uloo GmbH
        \href{https://play.google.com/store/apps/details?id=com.uloo}{\emph{"Uloo logo."}}
        Google Play Market, 2020.
        \bibitem{habitica-logo} HabitRPG, Inc.
        \href{https://play.google.com/store/apps/details?id=com.habitrpg.android.habitica}{\emph{"Habitica logo."}}
        Google Play Market, 2020.
        \bibitem{habitify-logo}
        Unstatic Ltd Co
        \href{https://play.google.com/store/apps/details?id=co.unstatic.habitify}{\emph{"Habitify logo."}}
        Google Play Market, 2020.
        \bibitem{ticktick-logo}
        Appest Inc.
        \href{https://play.google.com/store/apps/details?id=com.ticktick.task}{\emph{"TickTick logo."}}
        Google Play Market, 2020.
        \bibitem{habitshare-logo}
        Luke Bickston
        \href{https://play.google.com/store/apps/details?id=com.habitshareapp}{\emph{"HabitShare logo."}}
        Google Play Market, 2020.
        \bibitem{wiki-mvc}
        \href{https://en.wikipedia.org/wiki/Model\%E2\%80\%93view\%E2\%80\%93controller}{\emph{"Model–view–controller."}}
        Wikipedia.org, 2021.
        \bibitem{spring}
        \href{https://spring.io/}{\emph{"Spring framework."}}
        spring.io, 2021.
        \bibitem{django}
        \href{https://www.djangoproject.com/}{\emph{"Django framework."}}
        djangoproject.com, 2021.
        \bibitem{ruby}
        \href{https://spring.io/}{\emph{"Ruby On Rails framework."}}
        rubyonrails.org, 2021.
        \bibitem{wiki-srp}
        \href{https://en.wikipedia.org/wiki/Single-responsibility_principle}{\emph{"Single-responsibility principle."}}
        Wikipedia.org, 2021.
        \bibitem{kotlin}
        \href{https://kotlinlang.org/}{\emph{"Kotlin programming language."}}
        kotlinlang.org, 2021.
        \bibitem{postgresql}
        \href{https://www.postgresql.org/}{\emph{"PostgreSQL Relational Database."}}
        postgresql.org, 2021.
        \bibitem{kotlin-compile}
        \href{https://medium.com/@johnkorly/kotlin-vs-java-performance-drill-down-which-to-choose-2514bdf91916}{\emph{"Kotlin vs Java: Performance Drill down \& Which to choose."}}
        medium.com/@johnkorly, 2019.
        \bibitem{react}
        \href{https://reactjs.org/}{\emph{"React JavaScript library."}}
        reactjs.org, 2021.
        \bibitem{material}
        \href{https://material-ui.com/}{\emph{"Material-UI React library."}}
        material-ui.com, 2021.
        \bibitem{axios}
        \href{https://github.com/axios/axios}{\emph{"Axios JavaScript library."}}
        github.com/axios/axios, 2021.
        \bibitem{redux}
        \href{https://redux.js.org/}{\emph{"Redux React library."}}
        redux.js.org, 2021.
        \bibitem{react-native}
        \href{https://reactnative.dev/}{\emph{"React Native."}}
        redux.js.org, 2021.
        \bibitem{typescript}
        \href{https://www.typescriptlang.org/}{\emph{"TypeScript programming language."}}
        typescriptlang.org, 2021.
        \bibitem{heroku}
        \href{https://www.heroku.com/}{\emph{"Heroku cloud platform."}}
        heroku.com, 2021.
        \bibitem{heroku-vs-aws}
        \href{https://railsware.com/blog/heroku-vs-aws-which-paas-hosting-to-choose/}{\emph{"Heroku vs. AWS – Which PaaS Hosting to Choose?"}}
        railsware.com, 2018.
        \bibitem{spring-doc}
        \href{https://docs.spring.io/spring-framework/docs/current/reference/html/}{\emph{"Spring framework documentation"}}
        spring.io, 2021.
        \bibitem{baeldung}
        \href{https://www.baeldung.com/}{\emph{"Baeldung - Spring tutorials"}}
        baeldung.com, 2021.
%        \bibitem{wiki-mvc}
%        Wikipedia.org
%        \href{https://en.wikipedia.org/wiki/Model\%E2\%80\%93view\%E2\%80\%93controller}{\emph{"Model–view–controller."}}
%        Wikipedia.org, 2021.
%        \bibitem{color-psych} https://www.nickkolenda.com/color-psychology/#color-meanings-table
    \end{thebibliography}
\end{document}