%!TEX ROOT=main.tex

\section{Domain model}\label{sec:domain-model}

This section will describe entities of an application domain model in details.
Some technical information, as data types, are omitted for brevity.
Each entity will have information about creation date, modification date etc.

\subsection{User}\label{subsec:user}

User entity consists of a minimum required attributes in order to simplify registration process for end-user.
Recursive relation represents friendship between users, which is required for activity sharing.
Goal plans, goals and habits are always owned by one user and might be shared with many users.
Sharing is used for displaying private plans, goals and habits with specific users.

\subsection{Goal plan}\label{subsec:goal-plan}

Goal plan serves as a blueprint for a goal.
This separation of plan and goal allows users create and share not only their progress, but also plans themselves.
Possible use case would be the following.
A user is proficient in specific field or skill that other users would like to learn or gain.
They create a goal plan with tasks that contains instructions and share it with any amount of users.
Other users then able to start goal pursuing process using this shared plan.

\subsection{Goal}\label{subsec:goal}

Goal is a tool for managing long-term targets.
It is also a specific case of fulfilling a goal plan that is created by user or shared with them.

\subsection{Task}\label{subsec:task}

Task is a building block of a goal.
Task completion used for calculation of a goal progress.

\subsection{Goal daily progress}\label{subsec:goal-daily-progess}

This entity holds data about daily progress on a specific goal during given day.
It is then used for statistics calculation.

\subsection{Habit}\label{subsec:habit}

Habit is a tool for managing simple and repetitive targets.

\subsection{Habit schedule}\label{subsec:habit-schedule}

Each habit has a schedule.
At first it filled with default values, but it is possible for users to change them.

\subsection{Habit daily progress}\label{subsec:habit-daily-progress}

This entity holds data about daily progress on a specific habit.
It is then used for statistics calculation.

\subsection{Activity}\label{subsec:activity}

This entity holds data about user activities on goals and habits.
When goal or habit shared with user, he will see related activities.

\subsection{Comment}\label{subsec:comment}

It is possible to comment of activities in application and reply to commentaries.
Everyone who has access to an activity could see all the commentaries.